---
title: "Regression code ADI HV"
author: "Emerald Yuan"
date: "2024-03-27"
output: html_document
---

# Load Libraries 
```{r}
library(data.table)
library(lme4)
library(lmerTest)
library(dplyr)
library(parameters)
library(jtools)
library(sjPlot)
library(car)
library(tableone)
library(Hmisc)
library(corrplot)
library(ggplot2)
library(interactionR)
library(interactions)
library(readr)
library(writexl)
library(broom.mixed)
library(boot)
```


# Load dataset
```{r}
### Setting Working Directory Here ###
ADI_HV <- read.csv("data_11_20.csv") # N = 10114

data_2_14<- read.csv("data_2_14.csv") # full dataset including missing N = 11876

```

```{r}
data<-data_2_14
#MISSING DATA: * check the missing value for each variables of interest
# get the missing data for each variable
sub1 = data%>%dplyr::select(
                            age,sex,src_subject_id,
                            rel_family_id,
                            White_non_Hispanic,  Hispanic_ethnicity,
                            p_edu_highest,
                            demo_comb_income_v2,reshist_addr1_status,
                            reshist_addr1_adi_edu_h,
                            reshist_addr1_adi_income,
                            reshist_addr1_adi_in_dis,
                            
                            reshist_addr1_adi_home_o,
                            reshist_addr1_adi_unemp,
                            
                            reshist_addr1_adi_pov,
                            reshist_addr1_adi_b138,
                            
                            reshist_addr1_adi_sp,
                            reshist_addr1_adi_ncar,
                            
                            reshist_addr1_popdensity,
                            site,crpbi_y_ss_parent,rh,lh,icv,
                            srpf_y_ss_ses,         
)


apply(is.na(sub1),2,sum)
# Total 11876
summary(data$reshist_addr1_adi_b138) #654 NA???

summary(sub1$reshist_addr1_status!="OK") #703 not "OK"
table(sub1$reshist_addr1_status)



#MISSING DATA: 1. get rid of those with missing quality data for neighborhoods
sub<-subset(sub1, reshist_addr1_status=="OK")


apply(is.na(sub),2,sum)

#MISSING DATA: 2. get rid of those with missing data for other variables
sub1 = sub%>%dplyr::select( age,sex,src_subject_id,
                            rel_family_id,
                            White_non_Hispanic,
                            Hispanic_ethnicity,
                            p_edu_highest,
                            demo_comb_income_v2,
                            reshist_addr1_adi_edu_h,
                            reshist_addr1_adi_income,
                            reshist_addr1_adi_in_dis,
                            
                            reshist_addr1_adi_home_o,
                            reshist_addr1_adi_unemp,
                            
                            reshist_addr1_adi_pov,
                            reshist_addr1_adi_b138,
                            
                            reshist_addr1_adi_sp,
                            reshist_addr1_adi_ncar,
                            
                            reshist_addr1_popdensity,
                            site,crpbi_y_ss_parent,
                            rh,lh,icv,srpf_y_ss_ses,     
                          )%>%na.omit()

```

# normalize variables 
```{r}
#normalizing variables
sub1$agez<-scale(sub1$age,center=T,scale=T)
sub1$sexz<-scale(sub1$sex,center=T,scale=T)
sub1$rhz<-scale(sub1$rh,center=T,scale=T)
sub1$lhz<-scale(sub1$lh,center=T,scale=T)
sub1$icvz<-scale(sub1$icv,center=T,scale=T)

sub1$srpf_y_ss_sesz<-scale(sub1$srpf_y_ss_ses,center=T,scale=T)
sub1$demo_comb_income_v2z<-scale(sub1$demo_comb_income_v2,center=T, scale=T)

sub1$reshist_addr1_adi_unempz1<-scale(sub1$reshist_addr1_adi_unemp,center=T,scale=T)
sub1$reshist_addr1_adi_povz1<-scale(sub1$reshist_addr1_adi_pov,center=T,scale=T)
sub1$reshist_addr1_adi_spz1<-scale(sub1$reshist_addr1_adi_sp,center=T,scale=T)
sub1$reshist_addr1_adi_home_oz1<-scale(sub1$reshist_addr1_adi_home_o,center=T,scale=T)
sub1$reshist_addr1_adi_edu_h1<-scale(sub1$reshist_addr1_adi_edu_h,center=T,scale=T)
sub1$reshist_addr1_adi_income1<-scale(sub1$reshist_addr1_adi_income,center=T,scale=T)
sub1$reshist_addr1_adi_in_dis1<-scale(sub1$reshist_addr1_adi_in_dis,center=T,scale=T)
sub1$reshist_addr1_adi_b1381<-scale(sub1$reshist_addr1_adi_b138,center=T,scale=T)
sub1$reshist_addr1_adi_ncar1<-scale(sub1$reshist_addr1_adi_ncar,center=T,scale=T)

sub1$reshist_addr1_popdensityz1<-scale(sub1$reshist_addr1_popdensity,center=T,scale=T)

sub1$sf<-(sub1$reshist_addr1_adi_spz1-sub1$reshist_addr1_adi_home_oz1)/2
sub1$crpbi_y_ss_parentz<-scale(sub1$crpbi_y_ss_parent,center =T, scale = T)


# add parental education (high school graduated)
sub1$p_edu_hs<-ifelse(is.na(sub1$p_edu_highest),NA,
                                  ifelse(sub1$p_edu_highest>=13,1,0))
```

# Outcome : Left Hippocampal Volume
## Stepwise Elimination 
p < .157 
```{r}
# Full model LH
m<-lmer(lhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        # icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
          reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
          reshist_addr1_adi_povz1+
          reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
          reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
```
# List-wise deletion (poverty)
```{r}
m<-lmer(lhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
          reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
       #   reshist_addr1_adi_povz1+
          reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
          reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
round(confint(m),digits=2)
```
# List-wise deletion (poverty 138)
```{r}
m<-lmer(lhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
          reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
       #   reshist_addr1_adi_povz1+
       #   reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
          reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
round(confint(m),digits=2)
```

# List-wise deletion (ncar)
```{r}
m<-lmer(lhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
          reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
       #   reshist_addr1_adi_povz1+
       #   reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
      #   reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
round(confint(m),digits=2)
```
# List-wise deletion (income disparity)
```{r}
m<-lmer(lhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
       #   reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
       #   reshist_addr1_adi_povz1+
       #   reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
      #   reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square

round(confint(m),digits=2)
```
# After list-wise deletions p< 0.05
```{r}
# After list-wise deletions  LH
m<-lmer(lhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
         # reshist_addr1_adi_in_dis1+
         # reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
         # reshist_addr1_adi_povz1+
        #  reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square

round(confint(m),digits=2)
```
# adjusted
```{r}
# After list-wise deletions  LH adjusted
m<-lmer(lhz ~ 
          agez+ 
          sex+ 
          White_non_Hispanic+ 
          p_edu_hs +  
          demo_comb_income_v2z+ #
          icvz+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
         # reshist_addr1_adi_in_dis1+
         # reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
         # reshist_addr1_adi_povz1+
        #  reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
vif(m)
```


# bootstrap final left model 
# bootstrap 5000 ########### Takes A Long Time To Run ################
```{r}
set.seed(123)

# Bootstrapping 500
boot_m <- bootMer(m, FUN = fixef, nsim = 500)

# summary of boostrap results
summary(boot_m)

# Calculate 95% bootstrap confidence intervals
boot_ci <- t(sapply(1:ncol(boot_m$t), function(i) {
  quantile(boot_m$t[, i], c(0.025, 0.975))
}))

# Attach column names
colnames(boot_ci) <- c("Lower CI", "Upper CI")

# Combine original estimates and confidence intervals

coefficients_and_ci <- cbind(original = fixef(m), boot_ci)

# Display coefficients and confidence intervals
coefficients_and_ci 


original_coef <- fixef(m)

# Calculate p-values for each coefficient
p_values <- sapply(seq_along(original_coef), function(i) {
  original <- original_coef[i]
  boot_dist <- boot_m$t[, i]
  
  # Calculate the proportion of bootstrap samples greater or less than zero
  if (original > 0) {
    p_value <- mean(boot_dist <= 0)
  } else {
    p_value <- mean(boot_dist >= 0)
  }
  
  # Return the p-value
  p_value
})

summary_m <- summary(m)
original_p_values <- format(summary_m$coefficients[, "Pr(>|t|)"],scientific=FALSE)

boot_means <- colMeans(boot_m$t)
# Combine coefficients, confidence intervals, and p-values into a data frame
boot_results <- data.frame(
  Original = original_coef,
  Original_P_value = original_p_values,
  Bootstrapped_Mean = boot_means,
  Lower_CI = boot_ci[, 1],
  Upper_CI = boot_ci[, 2],
  P_Value = p_values
)

# Print the table
print(boot_results)


# Print the updated table
print(boot_results)

```
# Outcome : Right Hippocampus
## Stepwise Elimination 
p < .157 to obtain the lowest AIC 
```{r}
# Full model RH
m<-lmer(rhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
          reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
          reshist_addr1_adi_povz1+
          reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
          reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square

```

# deletion of ncar
```{r}
# Full model RH
m<-lmer(rhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
          reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
          reshist_addr1_adi_povz1+
          reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
confint(m)
```
# deletion of income disparity
```{r}
# Full model RH
m<-lmer(rhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
        #  reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
          reshist_addr1_adi_povz1+
          reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
confint(m)
```
# deletion of poverty
```{r}
# Full model RH
m<-lmer(rhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
        #  reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
        #  reshist_addr1_adi_povz1+
          reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
confint(m)
```
# deletion of poverty 138
```{r}
# Full model RH
m<-lmer(rhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
          reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
        #  reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
        #  reshist_addr1_adi_povz1+
        #  reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
confint(m)
```
# deletion of edu_h
```{r}
m<-lmer(rhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
        #  reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
        #  reshist_addr1_adi_in_dis1+
          reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
        #  reshist_addr1_adi_povz1+
        #  reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summary(m)
summ(m) # AIC and Pseudo-R square
confint(m)
```

```{r}
# after list-wise deletion
m<-lmer(rhz ~ 
          #age+
          #sex+
          #White_non_Hispanic+
         # p_edu_hs + 
         # demo_comb_income_v2+
        #  icv+
        #  reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
        #  reshist_addr1_adi_in_dis1+
        #  reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
        #  reshist_addr1_adi_povz1+
        #  reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)
summary(m)
summ(m)
confint(m)

```

# Adding Covariates
```{r}
# after list-wise deletion
m<-lmer(rhz ~ 
          agez+
          sex+
          White_non_Hispanic+
          p_edu_hs + 
          demo_comb_income_v2z+
          icvz+
        #  reshist_addr1_adi_edu_h1+
         reshist_addr1_adi_income1+
        #  reshist_addr1_adi_in_dis1+
         # reshist_addr1_adi_home_oz1+
          reshist_addr1_adi_unempz1+
        #  reshist_addr1_adi_povz1+
        #  reshist_addr1_adi_b1381+
          reshist_addr1_adi_spz1+
        #  reshist_addr1_adi_ncar1+
          (1 | rel_family_id)+(1 | site), data=sub1)

summ(m)
summary(m)
vif(m)

confint(m)
```


## bootstrap 5000 ########### Takes A Long Time To Run ################
```{r}
set.seed(123)

# Bootstrapping 5000 (This takes a long time to run)
boot_m <- bootMer(m, FUN = fixef, nsim = 5000)



# summary of boostrap results
summary(boot_m)

# Calculate 95% bootstrap confidence intervals
boot_ci <- t(sapply(1:ncol(boot_m$t), function(i) {
  quantile(boot_m$t[, i], c(0.025, 0.975))
}))

# Attach column names
colnames(boot_ci) <- c("Lower CI", "Upper CI")

# Combine original estimates and confidence intervals

coefficients_and_ci <- cbind(original = fixef(m), boot_ci)

# Display coefficients and confidence intervals
coefficients_and_ci 


original_coef <- fixef(m)

# Calculate p-values for each coefficient
p_values <- sapply(seq_along(original_coef), function(i) {
  original <- original_coef[i]
  boot_dist <- boot_m$t[, i]
  
  # Calculate the proportion of bootstrap samples greater or less than zero
  if (original > 0) {
    p_value <- mean(boot_dist <= 0)
  } else {
    p_value <- mean(boot_dist >= 0)
  }
  
  # Return the p-value
  p_value
})

summary_m <- summary(m)
original_p_values <- format(summary_m$coefficients[, "Pr(>|t|)"],scientific=FALSE)

boot_means <- colMeans(boot_m$t)
# Combine coefficients, confidence intervals, and p-values into a data frame
boot_results <- data.frame(
  Original = original_coef,
  Original_P_value = original_p_values,
  Bootstrapped_Mean = boot_means,
  Lower_CI = boot_ci[, 1],
  Upper_CI = boot_ci[, 2],
  P_Value = p_values
)

# Print the table
print(boot_results)

```

# interaction with school environment
```{r}
#interaction adjusted model with school environment
m<-lmer(rhz ~ 
          age+
          sex+
          White_non_Hispanic+
          p_edu_hs + 
          #FH_vsp +
          demo_comb_income_v2+
          icvz+
          #reshist_addr1_adi_edu_h+
          reshist_addr1_adi_income1+ #standardized
          #reshist_addr1_adi_in_dis+
          #reshist_addr1_adi_home_o+
          reshist_addr1_adi_unempz1+ #standardized
          #reshist_addr1_adi_pov+
          #reshist_addr1_adi_b138+
          reshist_addr1_adi_spz1*srpf_y_ss_sesz+ #standardized
          #reshist_addr1_adi_ncar

          (1 | rel_family_id)+(1 | site), data=sub1)
summary(m)
summ(m)
```

## bootstrap school environment
```{r}
## bootstrap 5000 ########### Takes A Long Time To Run ################

set.seed(123)

# Bootstrapping 5000 (This takes a long time to run)
boot_m <- bootMer(m, FUN = fixef, nsim = 5000)



# summary of boostrap results
summary(boot_m)

# Calculate 95% bootstrap confidence intervals
boot_ci <- t(sapply(1:ncol(boot_m$t), function(i) {
  quantile(boot_m$t[, i], c(0.025, 0.975))
}))

# Attach column names
colnames(boot_ci) <- c("Lower CI", "Upper CI")

# Combine original estimates and confidence intervals

coefficients_and_ci <- cbind(original = fixef(m), boot_ci)

# Display coefficients and confidence intervals
coefficients_and_ci 


original_coef <- fixef(m)

# Calculate p-values for each coefficient
p_values <- sapply(seq_along(original_coef), function(i) {
  original <- original_coef[i]
  boot_dist <- boot_m$t[, i]
  
  # Calculate the proportion of bootstrap samples greater or less than zero
  if (original > 0) {
    p_value <- mean(boot_dist <= 0)
  } else {
    p_value <- mean(boot_dist >= 0)
  }
  
  # Return the p-value
  p_value
})

summary_m <- summary(m)
original_p_values <- format(summary_m$coefficients[, "Pr(>|t|)"],scientific=FALSE)

boot_means <- colMeans(boot_m$t)
# Combine coefficients, confidence intervals, and p-values into a data frame
boot_results <- data.frame(
  Original = original_coef,
  Original_P_value = original_p_values,
  Bootstrapped_Mean = boot_means,
  Lower_CI = boot_ci[, 1],
  Upper_CI = boot_ci[, 2],
  P_Value = p_values
)

# Print the table
print(boot_results)

```


# interaction with family environment
```{r}
#interaction adjusted model with school environment
m<-lmer(rhz ~ 
          age+
          sex+
          White_non_Hispanic+
          p_edu_hs + 
          #FH_vsp +
          demo_comb_income_v2+
          icvz+
          #reshist_addr1_adi_edu_h+
          reshist_addr1_adi_income1+ #standardized
          #reshist_addr1_adi_in_dis+
          #reshist_addr1_adi_home_o+
          reshist_addr1_adi_unempz1+ #standardized
          #reshist_addr1_adi_pov+
          #reshist_addr1_adi_b138+
          reshist_addr1_adi_spz1*crpbi_y_ss_parentz+ #standardized
          #reshist_addr1_adi_ncar+
          icvz+
          (1 | rel_family_id)+(1 | site), data=sub1)
summary(m)
summ(m)
```
# bootstrap family environment
```{r}
## bootstrap 5000 ########### Takes A Long Time To Run ################

set.seed(123)

# Bootstrapping 5000 (This takes a long time to run)
boot_m <- bootMer(m, FUN = fixef, nsim = 5000)



# summary of boostrap results
summary(boot_m)

# Calculate 95% bootstrap confidence intervals
boot_ci <- t(sapply(1:ncol(boot_m$t), function(i) {
  quantile(boot_m$t[, i], c(0.025, 0.975))
}))

# Attach column names
colnames(boot_ci) <- c("Lower CI", "Upper CI")

# Combine original estimates and confidence intervals

coefficients_and_ci <- cbind(original = fixef(m), boot_ci)

# Display coefficients and confidence intervals
coefficients_and_ci 


original_coef <- fixef(m)

# Calculate p-values for each coefficient
p_values <- sapply(seq_along(original_coef), function(i) {
  original <- original_coef[i]
  boot_dist <- boot_m$t[, i]
  
  # Calculate the proportion of bootstrap samples greater or less than zero
  if (original > 0) {
    p_value <- mean(boot_dist <= 0)
  } else {
    p_value <- mean(boot_dist >= 0)
  }
  
  # Return the p-value
  p_value
})

summary_m <- summary(m)
original_p_values <- format(summary_m$coefficients[, "Pr(>|t|)"],scientific=FALSE)

boot_means <- colMeans(boot_m$t)
# Combine coefficients, confidence intervals, and p-values into a data frame
boot_results <- data.frame(
  Original = original_coef,
  Original_P_value = original_p_values,
  Bootstrapped_Mean = boot_means,
  Lower_CI = boot_ci[, 1],
  Upper_CI = boot_ci[, 2],
  P_Value = p_values
)

# Print the table
print(boot_results)

summ(boot_m)


```
# Interaction Plot for Family Environment

```{r}
# interaction adjusted for school environment and single parent
m<-lmer(rhz ~ 
          age+
          sex+
          White_non_Hispanic+
          p_edu_hs + 
          #FH_vsp +
          demo_comb_income_v2+
          icvz+
          #reshist_addr1_adi_edu_h+
          reshist_addr1_adi_income1+ #standardized
          #reshist_addr1_adi_in_dis+
          #reshist_addr1_adi_home_o+
          reshist_addr1_adi_unempz1+ #standardized
          #reshist_addr1_adi_pov+
          #reshist_addr1_adi_b138+
          reshist_addr1_adi_spz1*srpf_y_ss_sesz+ #standardized
          #reshist_addr1_adi_ncar

          (1 | rel_family_id)+(1 | site), data=sub1)


# Create the interact_plot
p<-interact_plot(m, pred = reshist_addr1_adi_spz1, modx = srpf_y_ss_sesz, interval = TRUE,
                   x.label = 'Neighborhood Single-Parent Household (z-score)', y.label = 'Right Hippocampal Volume (z-score)',
                   legend.main = 'Positive School Environment')
p

# Save the plot to a WMF file
ggsave("figureA.pdf",width = 6, height = 6) # save picture as in vector pdf file 

```


```{r}
#interaction adjusted model with school environment
m<-lmer(rhz ~ 
          age+
          sex+
          White_non_Hispanic+
          p_edu_hs + 
          #FH_vsp +
          demo_comb_income_v2+
          icvz+
          #reshist_addr1_adi_edu_h+
          reshist_addr1_adi_income1+ #standardized
          #reshist_addr1_adi_in_dis+
          #reshist_addr1_adi_home_o+
          reshist_addr1_adi_unempz1+ #standardized
          #reshist_addr1_adi_pov+
          #reshist_addr1_adi_b138+
          reshist_addr1_adi_spz1*crpbi_y_ss_parentz+ #standardized
          #reshist_addr1_adi_ncar+
          icvz+
          (1 | rel_family_id)+(1 | site), data=sub1)

# Create the interact_plot
p<-interact_plot(m, pred = reshist_addr1_adi_spz1, modx = crpbi_y_ss_parentz, interval = TRUE,
                   x.label = 'Neighborhood Single-Parent Household (z-score)', y.label = 'Right Hippocampal Volume (z-score)',
                   legend.main = 'Positive Family Environment')
p

# Save the plot to a WMF file
ggsave("figureB.pdf",width = 6, height = 6) # save picture as in vector pdf file 
```




