---
title: "ADV_HV_Missing_EY_0326"
author: "Emerald Yuan"
date: "2024-03-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# install packages
```{r}
#install.packages(GGally)
#install.packages(ggplot2)
#install.packages(finalfit)
```

```{r}
pacman::p_load(
  dplyr,
  rio,
  lme4,
  lmerTest,
  car,
  mediation,
  lmtest,
  lattice,
  irr,
  parameters,
  ggplot2,
  cowplot,
  finalfit,
  GGally,
  gridExtra)
```

Load dataset
```{r}
### Set your working directory here ###
setwd("")
ADI_HV <- read.csv("data_11_20.csv") # N = 10114

data_2_14<- read.csv("data_2_14.csv") # full dataset including missing N = 11876

```

# generate multirace from raw data and add on to data_2_14 --> data_2_14_2

demo race 
```{r}
# set working directory 
demo<-read.csv("ABCD Baseline data.csv")

colnames(demo)

race <- demo %>%
  dplyr::select(src_subject_id,12:30) 

str(race)
# Assuming your data frame is named 'race'

race_counts <- rowSums(dplyr::select(race,
                              White, Black_African, American_Indian, Alaska_Native, Native_Hawaiian,
                              Guamanian, Samoan, Other_Pacific_Islander, Asian_Indian, Chinese,
                              Filipino, Japanese, Korean, Vietnamese, Other_Asian, Other_Race
                              ))

data <- race %>%
  mutate(race = case_when(
    race_counts > 1 ~ 7, ## two or more races 
    White == 1 ~ 1, #white
    Black_African == 1 ~ 2, #black
    Asian_Indian == 1 | Chinese == 1 | Filipino == 1 | Japanese == 1 |
      Korean == 1 | Vietnamese == 1 | Other_Asian == 1 ~ 3, #asian
    
    American_Indian == 1 | Alaska_Native == 1 ~ 4, #American Indian or Alaskan Native
    
    Native_Hawaiian == 1 | Guamanian == 1 | Samoan == 1 |
      Other_Pacific_Islander == 1 ~ 5, #Native Hawaiian or Pacific islander
  #Others, Don't know, or not to answer, or NA. 
    TRUE ~ 6  # Don't know, not to answer or NA
  )) %>%
  tidyr::replace_na(list(race = 6))

table(data$race)

race<-data%>%
  dplyr::select(src_subject_id,race)

data_2_14_2<-left_join(data_2_14,race,by="src_subject_id")

write.csv(data_2_14_2,"data_2_14_2.csv")

data_2_14<-data_2_14_2

```


```{r}
# select the variables we used for analysis 
dataf<-data_2_14%>%
  dplyr::select(src_subject_id,age,sex,race,Hispanic_ethnicity, White_non_Hispanic, p_edu_high,p_edu_highest,demo_comb_income_v2,reshist_addr1_adi_edu_h, reshist_addr1_adi_income, reshist_addr1_adi_in_dis, reshist_addr1_adi_home_o, reshist_addr1_adi_unemp, reshist_addr1_adi_pov, reshist_addr1_adi_b138, reshist_addr1_adi_sp, reshist_addr1_adi_ncar, reshist_addr1_popdensity, site, crpbi_y_ss_parent, rh, lh, icv, srpf_y_ss_ses)
```

```{r}
datas<-dataf
datas$excluded<-ifelse(dataf$src_subject_id %in% ADI_HV$src_subject_id,0,1)

table(datas$excluded) # excluded 1762 

```

```{r}
data<-datas
# rename
sub <- data %>%
  rename(
    Percentage_HS_Diploma = reshist_addr1_adi_edu_h,
    Avg_Household_Income = reshist_addr1_adi_income,
    Income_Disparity = reshist_addr1_adi_in_dis,
    Percentage_Home_Owner = reshist_addr1_adi_home_o,
    Percentage_Unemployed = reshist_addr1_adi_unemp,
    Percentage_Below_Poverty = reshist_addr1_adi_pov,
    Percentage_Below_138_Poverty = reshist_addr1_adi_b138,
    Percentage_Single_Parents = reshist_addr1_adi_sp,
    Percentage_No_Car = reshist_addr1_adi_ncar,
    Population_Density = reshist_addr1_popdensity,
    Right_Hippocampal_Volume=rh,
    Left_Hippocampal_Volume=lh
  )
sub1 <- sub %>%
  rename(
    age = age,
    combined_income = demo_comb_income_v2,
    Intracranial_Volume = icv,
    Positive_Family_Environment = crpbi_y_ss_parent,
    Positive_School_Environment = srpf_y_ss_ses
  )

sub2<-sub1%>%
  mutate(high_school=ifelse(p_edu_highest>=13,1,0)) # at least high school graduate


# recreate categorical variables 
sub2$Sex <- factor(sub2$sex, levels = c(0, 1), labels = c("Female", "Male")) # female and male 
sub2$White_Non_Hispanic <- factor(sub2$White_non_Hispanic, levels = c(0, 1), labels = c("Minority", "White")) # minority and white non-hispanic
sub2$Parental_High_School<-factor(sub2$high_school, levels = c(0,1), labels = c("No", "Yes"))
categorical_predictors<-c("sex_c","White_non_Hispanic_c","high_school_c")
ADI <- c("Percentage_HS_Diploma", 
                           "Avg_Household_Income", "Income_Disparity", 
                           "Percentage_Home_Owner", "Percentage_Unemployed", 
                           "Percentage_Below_Poverty", "Percentage_Below_138_Poverty",
                           "Percentage_Single_Parents", "Percentage_No_Car"
                          )


outcomes<-c("Right_Hippocampal_Volume", "Left_Hippocampal_Volume")

key_missing<-c("combined_income","Right_Hippocampal_Volume", "Left_Hippocampal_Volume","Percentage_Single_Parents")

demo<-c("age", "Sex","White_Non_Hispanic","Parental_High_School",
                           "Positive_School_Environment", "Positive_Family_Environment","Intracranial_Volume")
```

```{r}
table(sub2$combined_income,useNA="ifany") #1018 missing
summary(sub2$Percentage_HS_Diploma,useNA="ifany") # 654 missing 

sub2<-sub2%>%
  mutate(ADI = Percentage_HS_Diploma+Avg_Household_Income+Income_Disparity+Percentage_Home_Owner +Percentage_Unemployed+
           Percentage_Below_Poverty+Percentage_Below_138_Poverty+Percentage_Single_Parents+Percentage_No_Car)

key_missing<-c("combined_income","Right_Hippocampal_Volume", "Left_Hippocampal_Volume","ADI")

missing<-c("combined_income","Right_Hippocampal_Volume", "Left_Hippocampal_Volume","ADI")
```

## Comparison of Missing Values Among Demographic Variables
```{r echo=FALSE}
# z score all continuous variables 
vars <- c(
  "age","combined_income",
  
  "Positive_Family_Environment", 
  "Positive_School_Environment", 
  
  "Percentage_HS_Diploma", 
  "Avg_Household_Income", 
  "Income_Disparity", 
  "Percentage_Home_Owner", 
  "Percentage_Unemployed", 
  "Percentage_Below_Poverty", 
  "Percentage_Below_138_Poverty", 
  "Percentage_Single_Parents", 
  "Percentage_No_Car", 
  
  "Right_Hippocampal_Volume", 
  "Left_Hippocampal_Volume", 
  "Intracranial_Volume","ADI"
)
sub2_z <-sub2 # create a sub2_z for all z-scored continuous variables 
sub2_z[vars] <- scale(sub2[vars], center = TRUE, scale = TRUE)


p<-sub2_z %>% 
  missing_pairs(key_missing,demo)

p<-p+ggplot2::theme(
 plot.title = ggplot2::element_text(size = 15),  # Title size
  axis.text = ggplot2::element_text(size = 9),   # Axis text size
  axis.title = ggplot2::element_text(size = 18),   # Axis title size
)

#ggsave("Missing_demo_compare.png", p, width = 24, height = 13, units = "in", dpi = 300)



```

# Comparison of Missing Values Among ADIs 
## compare if missing data in neighborhood characteristics influence right HV or Left HV

```{r}
# rename ADIs 

sub3<-sub2_z%>%
  rename(Percent_HS_Diploma = Percentage_HS_Diploma,
    Percent_Home_Owner = Percentage_Home_Owner ,
    Percent_Unemployed = Percentage_Unemployed,
    Percent_Below_Poverty = Percentage_Below_Poverty,
    Percent_Below_138_Poverty = Percentage_Below_138_Poverty,
    Percent_Single_Parents = Percentage_Single_Parents,
    Percent_No_Car = Percentage_No_Car,

    
    Right_HV= Right_Hippocampal_Volume,
    Left_HV = Left_Hippocampal_Volume)



missing_adi<-c("combined_income","Left_HV","Right_HV")

ADI <- c("Percent_HS_Diploma", 
                           "Avg_Household_Income", "Income_Disparity", 
                           "Percent_Home_Owner", "Percent_Unemployed", 
                           "Percent_Below_Poverty", "Percent_Below_138_Poverty",
                           "Percent_Single_Parents", "Percent_No_Car"
                          )

p<-sub3 %>% 
  missing_pairs(missing_adi, ADI)
p<-p+ggplot2::theme(
 plot.title = ggplot2::element_text(size = 20),  # Title size
  axis.text = ggplot2::element_text(size = 12),   # Axis text size
  axis.title = ggplot2::element_text(size = 20),   # Axis title size
)

# ggsave("Missing_ADI_compare.png", p, width = 20, height = 12, units = "in", dpi = 300)
```


# QQ plot for no missing and missing data
```{r echo=FALSE}
vars <- c("age","combined_income",
  "Positive_Family_Environment", 
  "Positive_School_Environment", 
  "Percentage_HS_Diploma", 
  "Avg_Household_Income", 
  "Income_Disparity", 
  "Percentage_Home_Owner", 
  "Percentage_Unemployed", 
  "Percentage_Below_Poverty", 
  "Percentage_Below_138_Poverty", 
  "Percentage_Single_Parents", 
  "Percentage_No_Car", 
  "Right_Hippocampal_Volume", 
  "Left_Hippocampal_Volume", 
  "Intracranial_Volume"
)


qq_plot_func <- function(included_data, excluded_data, var) {
  # Extract the variable values for included and excluded datasets
  included_var <- included_data %>% pull(var) %>% unlist()
  excluded_var <- excluded_data %>% pull(var) %>% unlist()
  
  # Generate the Q-Q plot
  qq.out <- qqplot(x = included_var, y = excluded_var, plot.it = FALSE)
  qq.out <- as.data.frame(qq.out)
  names(qq.out) <- c("Included", "Excluded")
  
  # Set the x and y limits
  xylim <- range(c(qq.out$Included, qq.out$Excluded), na.rm = TRUE)
  
  # Plot the Q-Q plot
  ggplot(qq.out, aes(x = Included, y = Excluded)) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1) +
    coord_fixed(ratio = 1, xlim = xylim, ylim = xylim) +
    ggtitle(paste0("Empirical Q-Q Plot for ", var))+
    theme(plot.title=element_text(size=10))
}
sub2_missing<-sub2_z%>%
  filter(excluded==1)

# Apply the function to each variable in the vars list
qq_plots <- lapply(vars, function(x) qq_plot_func(sub2_z, sub2_missing, x))

# Arrange QQ plots in a grid
qq_plot_grid <- grid.arrange(grobs = qq_plots, ncol = 4)

# Save the plot grid to a PDF file
#ggsave("qq_plot_grid.pdf", qq_plot_grid, width = 20, height = 10)

ggsave("qq_plot_grid.png", qq_plot_grid, width = 16, height = 14, dpi=300)
```


# stable 1 comparison between missing values
```{r echo=FALSE}

library(tableone)
allvars <- c("age", "sex","race",'Hispanic_ethnicity',"White_non_Hispanic","p_edu_high","demo_comb_income_v2", "reshist_addr1_popdensity",
             "reshist_addr1_adi_edu_h",
             "reshist_addr1_adi_income",
             "reshist_addr1_adi_in_dis", "reshist_addr1_adi_home_o",
             "reshist_addr1_adi_unemp", "reshist_addr1_adi_pov",
             "reshist_addr1_adi_b138", "reshist_addr1_adi_sp",
             "reshist_addr1_adi_ncar","icv","lh","rh",
             "srpf_y_ss_ses","crpbi_y_ss_parent")

catvars <- c("sex","race",'Hispanic_ethnicity',"White_non_Hispanic","p_edu_high")
non<-c("age","lh","rh","icv","reshist_addr1_adi_edu_h",
       "reshist_addr1_adi_income",
       "reshist_addr1_adi_in_dis",
       "reshist_addr1_adi_home_o", "reshist_addr1_adi_unemp", "reshist_addr1_adi_pov",
       "reshist_addr1_adi_b138","reshist_addr1_adi_sp",
       "reshist_addr1_adi_ncar", "reshist_addr1_popdensity","srpf_y_ss_ses","demo_comb_income_v2","crpbi_y_ss_parent")
stab2 <- CreateTableOne(vars = allvars , strata = "excluded", data = datas,factorVars = catvars)
st1<-print(stab2,nonnormal = non, showAllLevels = FALSE, formatOptions = list(big.mark = ",", scientific = FALSE))
```







