---
title: "ADI HV Plots"
author: "Emerald Yuan"
date: "2024-03-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
install packages
```{r}

library(ggplot2)
library(GGally)
```


```{r}
pacman::p_load(
  dplyr,
  rio,
  lme4,
  lmerTest,
  car,
  mediation,
  lmtest,
  lattice,
  irr,
  parameters,
  ggplot2,
  cowplot,
  finalfit,
  GGally)
```


Load dataset
```{r}
setwd("C:/Users/qyuan25/OneDrive - Emory University/Shared Documents - SOM Ku Lab/General/ABCD Data/ADI, HV, and Positive Family and School Environment")

ADI_HV <- read.csv("C:/Users/qyuan25/OneDrive - Emory University/Shared Documents - SOM Ku Lab/General/ABCD Data/ADI, HV, and Positive Family and School Environment/data_11_20.csv") # N = 10114
data<-ADI_HV
```

# Rename Variables for Plots
```{r pressure, echo=FALSE}

# rename
sub <- data %>%
  rename(
    #demo
    age = age,
    combined_income = demo_comb_income_v2,
    # Moderators
    Positive_Family_Environment = crpbi_y_ss_parent,
    Positive_School_Environment = srpf_y_ss_ses,
    # ADI
    Percentage_HS_Diploma = reshist_addr1_adi_edu_h,
    Avg_Household_Income = reshist_addr1_adi_income,
    Income_Disparity = reshist_addr1_adi_in_dis,
    Percentage_Home_Owner = reshist_addr1_adi_home_o,
    Percentage_Unemployed = reshist_addr1_adi_unemp,
    Percentage_Below_Poverty = reshist_addr1_adi_pov,
    Percentage_Below_138_Poverty = reshist_addr1_adi_b138,
    Percentage_Single_Parents = reshist_addr1_adi_sp,
    Percentage_No_Car = reshist_addr1_adi_ncar,
    Population_Density = reshist_addr1_popdensity,
    # BOI
    Right_Hippocampal_Volume=rh,
    Left_Hippocampal_Volume=lh,
    Intracranial_Volume = icv,
  )

sub1<-sub%>%
  mutate(p_high_school=ifelse(p_edu_highest>=13,1,0)) # at least high school graduate

```
# Check Numeric and Factors
```{r}
is.numeric(sub1$age)
is.factor(sub1$sex)
is.factor(sub1$White_non_Hispanic)
is.factor(sub1$p_high_school)
is.numeric(sub1$combined_income)

vars <- c(
  "Positive_Family_Environment", 
  "Positive_School_Environment", 
  "Percentage_HS_Diploma", 
  "Avg_Household_Income", 
  "Income_Disparity", 
  "Percentage_Home_Owner", 
  "Percentage_Unemployed", 
  "Percentage_Below_Poverty", 
  "Percentage_Below_138_Poverty", 
  "Percentage_Single_Parents", 
  "Percentage_No_Car", 
  "Population_Density", 
  "Right_Hippocampal_Volume", 
  "Left_Hippocampal_Volume", 
  "Intracranial_Volume"
)

# Check if variables are numeric
is_numeric <- sapply(sub1[vars], is.numeric)

# Print the result
print(is_numeric)

```

# Change format of these variables one by one
```{r}
sub2 <- sub1 %>%
  mutate(sex=as.factor(sex),
         White_non_Hispanic = as.factor(White_non_Hispanic),
         p_high_school = as.factor(p_high_school)
  )

str(sub2)

```

# Check Numeric and Factors again
```{r}

is.factor(sub2$sex)
is.factor(sub2$White_non_Hispanic)
is.factor(sub2$p_high_school)


vars <- c(
  "age","combined_income",
  
  "Positive_Family_Environment", 
  "Positive_School_Environment", 
  
  "Percentage_HS_Diploma", 
  "Avg_Household_Income", 
  "Income_Disparity", 
  "Percentage_Home_Owner", 
  "Percentage_Unemployed", 
  "Percentage_Below_Poverty", 
  "Percentage_Below_138_Poverty", 
  "Percentage_Single_Parents", 
  "Percentage_No_Car", 
  
  "Right_Hippocampal_Volume", 
  "Left_Hippocampal_Volume", 
  "Intracranial_Volume"
)

# Check if variables are numeric
is_numeric <- sapply(sub2[vars], is.numeric)

# Print the result
print(is_numeric)

```
# Rescale all continuous variables  put the z scored into sub2_z
```{r}
sub2_z <-sub2 # create a sub2_z for all z-scored continuous variables 
sub2_z[vars] <- scale(sub2[vars], center = TRUE, scale = TRUE)

summary(sub2[vars])
summary(sub2_z[vars])

```
# Relabel categorical variables 
```{r}
# recreate categorical variables 
sub2$sex <- factor(sub2$sex, levels = c(0, 1), labels = c("Female", "Male")) 
sub2$White_non_Hispanic <- factor(sub2$White_non_Hispanic, levels = c(0, 1), labels = c("Ethno-racial Minority", "non-Hispanic White"))
sub2$p_high_school <-factor(sub2$p_high_school, levels = c(0,1), labels = c("Parents without high school diploma", "Parents with high school diploma"))

# relabel z-score abbreviations 
sub2_z$sex <- factor(sub2_z$sex, levels = c(0, 1), labels = c("Female", "Male")) 
sub2_z$White_non_Hispanic <- factor(sub2_z$White_non_Hispanic, levels = c(0, 1), labels = c("Min", "White"))
sub2_z$p_high_school <-factor(sub2_z$p_high_school, levels = c(0,1), labels = c("Parents no high school", "Parents with high school diploma"))

```

# Histograms for all variables 
```{r}
# Loop through each variable to create standardized histograms
for (variable in vars) {
  # Create histogram using ggplot2
  plot<-ggplot(sub2, aes_string(x = variable)) +
    geom_histogram(fill = "skyblue", color = "black", bins = 30)
    
  print(plot)
  # save each histogram to a file
   ggsave(filename = paste(variable, ".png", sep = ""), plot = last_plot(),height = 3, width = 5)
}

```

# Predictors (categorical, boxplot): Sex, White Non-Hispanic, parental high education
## Outcome: Left Hippocampal Volume
```{r}
categorical_predictors<-c("sex","White_non_Hispanic","p_high_school")
# Create boxplots for each categorical predictor against the outcome variable

for (predictor in categorical_predictors) {
  # Create boxplot
  boxplot <- ggplot(sub2, aes_string(x = predictor, y = "Left_Hippocampal_Volume")) +
    geom_boxplot() +
    labs( x = predictor, y = "Left Hippocampal Volume")
  
  # Print boxplot
  print(boxplot)
  
  # Save boxplot with smooth edges
   ggsave(filename = paste("Left Hippocampal Volume",predictor, "_boxplot.png"), plot = boxplot ,height = 3, width = 5, dpi = 300)
}
```

## Outcome : Right Hippocampal Volume
```{r}
categorical_predictors<-c("sex","White_non_Hispanic","p_high_school")
# Create boxplots for each categorical predictor against the outcome variable

for (predictor in categorical_predictors) {
  # Create boxplot
  boxplot <- ggplot(sub2, aes_string(x = predictor, y = "Right_Hippocampal_Volume")) +
    geom_boxplot() +
    labs( x = predictor, y = "Right Hippocampal Volume")
  
  # Print boxplot
  print(boxplot)
  
  # Save boxplot with smooth edges
   ggsave(filename = paste("Right Hippocampal Volume",predictor, "_boxplot.png"), plot = boxplot ,height = 3, width = 5, dpi = 300)
}
```

# Pairwise comparison of continuous predictors
```{r}
continuous_predictors <- c("age", "combined_income", "Percentage_HS_Diploma", 
                           "Avg_Household_Income", "Income_Disparity", 
                           "Percentage_Home_Owner", "Percentage_Unemployed", 
                           "Percentage_Below_Poverty", "Percentage_Below_138_Poverty",
                           "Percentage_Single_Parents", "Percentage_No_Car", 
                           "Positive_School_Environment", "Positive_Family_Environment","Intracranial_Volume")

categorical_predictors<-c("sex","White_non_Hispanic","p_high_school")

```

Left and Right Hippocampal Pairwise plots (z-scored)
# sample sub2_z 
## ADI
```{r}

# Abbreviations for Hippocampal Volume
sub2_z$Right_HV<-sub2_z$Right_Hippocampal_Volume
sub2_z$Left_HV<-sub2_z$Left_Hippocampal_Volume
 
   ADI<-sub2_z%>%
  dplyr::select(Percentage_HS_Diploma, 
                           Avg_Household_Income, Income_Disparity, 
                           Percentage_Home_Owner, Percentage_Unemployed, 
                           Percentage_Below_Poverty, Percentage_Below_138_Poverty,
                           Percentage_Single_Parents, Percentage_No_Car,Left_HV, Right_HV)

g = ggpairs(ADI, columns = 1:11, 
        lower = list(
          continuous = function(data, mapping, ...) {
            ggplot(data = data, mapping = mapping) + 
              geom_point(size = 0.3) + 
              geom_smooth(method = lm, size = 0.8, level=0.95, se = TRUE, color = "royalblue", fill = "brown", verbose=FALSE) + # 95% Confidence Bands
              theme(
                plot.title = element_text(size = 15),  # Title size
                axis.text = element_text(size = 12),   # Axis text size
                axis.title = element_text(size = 14)   # Axis title size
              )
          }
        ))
          

g
#ggsave("large_pairwise_plot_ADI_HV.png", g, width = 20, height = 13, units = "in", dpi = 300)
```
# Demographic Characteristics 
```{r}
 
   Covariates<-sub2_z%>%
  dplyr::select(age,combined_income,Positive_Family_Environment,Positive_School_Environment,
                Intracranial_Volume,Right_HV,Left_HV)


g = ggpairs(Covariates, columns = 1:7, upper = "blank",
        lower = list(
          continuous = function(data, mapping, ...) {
            ggplot(data = data, mapping = mapping) + 
              geom_point(size = 0.3) + 
              geom_smooth(method = lm, size = 0.8, level=0.95, se = TRUE, color = "royalblue", fill = "brown", verbose=FALSE)})  # 95% Confidence Bands
   
        )

g<-g+ggplot2::theme(
                plot.title = element_text(size = 18),  # Title size
                axis.text = element_text(size = 12),   # Axis text size
                axis.title = element_text(size = 20)   # Axis title size
              )

g
#ggsave("large_plot_covariates.png", g, width = 16, height = 10, units = "in", dpi = 300)
```

# ADI and Moderators 
```{r}
 
   ADI_mod<-sub2_z%>%
  dplyr::select(Positive_Family_Environment,Positive_School_Environment,Percentage_HS_Diploma, 
                           Avg_Household_Income, Income_Disparity, 
                           Percentage_Home_Owner, Percentage_Unemployed, 
                           Percentage_Below_Poverty, Percentage_Below_138_Poverty,
                           Percentage_Single_Parents, Percentage_No_Car
    )

## upper scatterplots
g = ggpairs(ADI_mod, columns = 1:11, 
        upper = list(
          continuous = function(data, mapping, ...) {
            ggplot(data = data, mapping = mapping) + 
              geom_point(size = 0.3) + 
              geom_smooth(method = lm, size = 0.8, level=0.95, se = TRUE, color = "royalblue", fill = "brown", verbose=FALSE)}),# 95% Confidence Bands
        lower = list(continuous="cor") 
   
        )

g<-g+ggplot2::theme(
                plot.title = element_text(size = 20),  # Title size
                axis.text = element_text(size = 15),   # Axis text size
                axis.title = element_text(size = 20)   # Axis title size
              )

g
#ggsave("large_plot_ADI_mod.png", g, width = 20, height = 18, units = "in", dpi = 300)
```

```{r}
## upper correlation coefficients 
g = ggpairs(ADI_mod, columns = 1:11, 
        
        upper = list(continuous="cor") ,
         lower = list(
          continuous = function(data, mapping, ...) {
            ggplot(data = data, mapping = mapping) + 
              geom_point(size = 0.3) + 
              geom_smooth(method = lm, size = 0.8, level=0.95, se = TRUE, color = "royalblue", fill = "brown", verbose=FALSE)}),# 95% Confidence Bands
   
        )

g<-g+ggplot2::theme(
                plot.title = element_text(size = 20),  # Title size
                axis.text = element_text(size = 15),   # Axis text size
                axis.title = element_text(size = 20)   # Axis title size
              )

g
#ggsave("large_plot_ADI_mod_upper.png", g, width = 20, height = 18, units = "in", dpi = 300)
```




